\documentclass{article}
\newcommand{\name}{Andrew Mcveigh}
\newcommand{\street}{Sint-Gilliskerkstraat 57}
\newcommand{\citycountry}{1000 Brussels, Belgium}
\newcommand{\phone}{+32.497.471.609}
\newcommand{\email}{me@andrewmcveigh.com}
\newcommand{\web}{www.andrewmcveigh.com}
\newcommand{\twitter}{twitter.com/andrewmcveigh}
\newcommand{\github}{github.com/andrewmcveigh}
\usepackage{geometry}
\geometry{a4paper,tmargin=50mm,bmargin=30mm,lmargin=25mm,rmargin=25mm,headheight=30mm,headsep=10mm,footskip=10mm}
\usepackage{fancyhdr,lastpage}
\pagestyle{fancyplain}
\fancyhf{}
\rhead{\small\name\\\street\\\citycountry\\\phone\\\\\email\\\web}
\rfoot{\scriptsize{Page \thepage\ of \pageref{LastPage}}}
\renewcommand\headrulewidth{0pt}

\title{Curriculum Vitae}
\author{Andrew Mcveigh}
\date{}

\begin{document}

\maketitle







\title{\vspace{-10mm}}



\section*{Education}
\label{sec-1}

\subsection*{Acedemic Qualifications}
\label{sec-1.1}

\subsubsection*{\emph{University of Huddersfield, England}}
\label{sec-1.1.1}

\begin{itemize}
\item BSc Software Development \& Multimedia (1st Class), 2008
\end{itemize}
\subsubsection*{\emph{Huddersfield Technical College}}
\label{sec-1.1.2}

\begin{itemize}
\item Diploma, Access Studies (Computing/Maths/Chemistry), 2004
\end{itemize}
\subsubsection*{\emph{Salendine Nook High School}}
\label{sec-1.1.3}

\begin{itemize}
\item 8 GCSEs (Grades A-C), 1998
\end{itemize}
\subsection*{Professional Qualifications}
\label{sec-1.2}

\subsubsection*{\emph{Microsoft Certified Professional}}
\label{sec-1.2.1}

\begin{itemize}
\item Networking Essentials, 2000
\end{itemize}
\section*{Technical Summary}
\label{sec-2}

\subsection*{Languages / Frameworks}
\label{sec-2.1}

Clojure, C\#, Java, Javascript, Python, Bash, SQL, HTML, HAML, CSS, SASS, ASP.NET(MVC), .NET, Silverlight, jQuery, Django, Cocoa, Objective-C, AppleScript, Tex/laTex
\subsection*{Operating Systems, Software and Technologies}
\label{sec-2.2}

Linux, OS X, Windows (NT/2000/XP/Sever/Vista/7), Vim, Visual Studio, Netbeans, Eclipse, Git, Mercurial, Subversion, Maven, Puppet, Apache, IIS, Lighttpd, Nginx, MongoDB, SQLite, MySQL, PostgreSQL, SQL Server, Flash, Photoshop, Illustrator, VMWare, MS Exchange
\section*{Experience}
\label{sec-3}

\subsection*{Software Developer}
\label{sec-3.1}

\subsubsection*{\emph{Interel Group, Brussels  [2008 - Present]}}
\label{sec-3.1.1}

Hired on an IT helpdesk/software development student placement, later offered a full-time position as a software developer. Now responsible for the design, development, and maintenance of all the group's software infrastructure.
\begin{itemize}
\item Delivered a customised implementation of an ``XWiki Farm''. [Java/J2EE/Clojure]
\item Client Wins: Simple CRUD webapp with Javascript image editor [C\#/ASP.NET MVC/Javascript/T-SQL]
\item Helpdesk ticketing webapp. [C\#/ASP.NET MVC/Javascript/T-SQL]
\item helpdesk.mail: Monitors an Exchange mailbox for emails, adds a logs in the ticketing system. [Clojure/SOAP/Exchange Web Services API]
\item Inventory tracking webapp, integrated with the Intranet, and the ticketing system. [C\#/ASP.NET MVC/Javascript/T-SQL]
\item TAPI Monitor: Monitors a VOIP extention for incoming calls, looks up caller from called id, logs in ticketing system. [TAPI/C\#/.NET]
\item Maintenance of the company Intranet [VB.NET/Javascript]
\item Building reports on various existing databases. [C\#/Crystal Reports/Clojure/Incanter]
\item Financial report building [Business Objects/AnalytiX]
\item Distributed configuration managment of various *NIX based servers. [Puppet]
\item Various scripting/sysadmin tasks [Bash/Python/*NIX]
\end{itemize}
\subsection*{Sales Assistant}
\label{sec-3.2}

\subsubsection*{\emph{Gamestation, Huddersfield [2005 - 2006]}}
\label{sec-3.2.1}

Duties/responsibilities: staff training, stock control, cashing up, banking, administration, and customer service.
\subsection*{Shift Manager}
\label{sec-3.3}

\subsubsection*{\emph{Allied Leisure, Huddersfield [2001 - 2004]}}
\label{sec-3.3.1}

Duties/responsibilities: staff management, staff training, stock control, ordering, cashing up, banking, loss control, administration, and customer service.
\subsection*{Insurance Assistant}
\label{sec-3.4}

\subsubsection*{\emph{Fartown Insurance, Huddersfield [2000 - 2001]}}
\label{sec-3.4.1}

Duties/responsibilities: customer quotations, renewals, developing and maintaining the company website, other general administration duties.
\subsection*{Computer Technician}
\label{sec-3.5}

\subsubsection*{\emph{Easy Computers, Huddersfield [1998 - 2000]}}
\label{sec-3.5.1}

Duties/responsibilities: build, repair, update and install home computers, on-site network installation and maintenance.

\end{document}
